---
title: "Homework_2"
author: "Emily Ogden"
date: "January 15, 2020"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```
#Scenario 1  
a)  
$H_0:\mu_{2009}=\mu_{2010}$  
$H_A:\mu_{2009}\neq\mu_{2010}$  

b)  
```{r}
catch1=c(91900,95200,61900,73600,114300,117000,129500,74200,112700,152100,90700,89400,127500,142200)
catch2=c(82900,86700,46900,41300,91600,100400,128400,55900,101700,139100,79300,76100,114100,139800)
hist(catch1,main="",xlab="2009 catch (tonnes)")
hist(catch2,main="",xlab="2010 catch (tonnes)")
```
  
c) A paired two-sample t-test would be best for this scenario, because each year's catch is by village.

d)  
```{r}
t.test(catch1,catch2,paired=T)
```
  
e)
```{r}
qt(0.95,13)
```

$t_{obs}=6.38$
$t_{crit}=1.77$

f)  
Both $t_{obs}>t_{crit}$ and p<0.05, indicating that there is evidence to reject the null hypothesis that the mean catch from 2009 and 2010 are equal. 

#Scenario 2
a)  
$H_0:\mu=15$  
$H_A:\mu>15$  
b)  
```{r}
P=c(18.4,12.9,15.3,18.3,15.6,23.3,16.5,12.3,24.6,16.2)
hist(P,main="",xlab=expression(paste("Total phosphorus (",mu,"g/L)")))
```
  
c)  
A one-sample t-test would be best for this scenario.  
d)  
```{r}
t.test(P,mu=15)
0.09794/2
```
  
e)  
```{r}
qt(0.95,9)
```
$t_{obs}=1.8462$
$t_{crit}=1.8331$  
f)  
Both $t_{obs}>t_{crit}$ and p=0.048 which indicates that there is evidence to reject the null hypothesis that the mean phosphorus levels are equal to 15 $\mu$g/L.Therefores there is evidence to support the alternative hypothesis that the mean phosphorus levels are greater than 15 $\mu$g/L.

#Scenario 3  
a)  
$H_0:\mu_a=\mu_b$  
$H_A:\mu_a\neq\mu_b$  
b)  
```{r}
meat=c(2.3,1.8,1.9,1.8,2.1,2.3,2.0,2.2,2.2,1.5,1.8,2.1,2.3,2.2,2.3)
veg=c(1.6,1.1,0.7,1.0,1.0,0.9,1.2,0.8,0.9,0.6,0.7,0.6,0.8,0.8,1.1)
hist(meat,main="",xlab="Carnivorous diet growth rates (% body weight/day)")
hist(veg, main = "",xlab="Vegetarian diet growth rates (% body weight/day)")
```
  
c)  
An independent two sample t-test would be best for this scenario. 
d)  
```{r}
t.test(meat,veg)
```
  
e)  
```{r}
qt(0.95,27)
```
$t_{obs}=12.237$
$t_{crit}=1.7032$  
f)  
Both $t_{obs}>t_{crit}$ and p<0.05, indicating that there is evidence to reject the null hypothesis that the mean growth rates are the same between carnivorous and vegetarian supplements.

#Scenario 4  
a)  
$H_0:$PCB poisoning is independent of trophic level  
$H_A:$PCB poisoning is dependent on trophic level  
b)  
```{r}
level1=c(133,100,17)
top=c(4,61,35)
poison=data.frame(level1,top)
poison
```
  
c)  
A Chi-squared test would be best for this scenario.  
d)  
```{r}
chisq.test(poison)
```
  
e)  
```{r}
qchisq(0.95,2)
```
$X^2_{obs}=89.253$
$X^2_{crit}=5.9914$   
f)   
Both $X^2_{obs}>X^2_{crit}$ and p<0.05, indicating that there is evidence to reject the null hypothesis that PCB poisoning is independent of trophic level.